%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Research and Development Engineer} % Job title
    {Synopsys Inc.} % Organization
    {Taipei, Taiwan} % Location
    {Dec. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed new features in NetTran, a gate-level netlist translator, to meet customer requirements and improve product functionality.}
        \item {Diagnosed and resolved customer-reported bugs, delivering prompt and effective solutions to ensure seamless operation.}
        \item {Enhanced ICV\_Netlist’s performance by addressing bottlenecks and mitigating I/O overhead with in-memory caching, resulting in a \textbf{71\%} reduction in runtime.}
        \item {Optimized NetTran’s performance by designing a high-scalability and disk-friendly threading architecture, reducing writing stage time by \textbf{76\%} and overall runtime by \textbf{34\%}.}
        \item {Implemented a thread-safe and high-scalability hash table, minimizing lock contention through fine-grained locking and atomic operations, achieving a \textbf{4.32×} performance boost.}
        \item {Collaborated with AE and QA teams to design a new debugging file in NetTran, helping customers quickly identify and resolve issues.}
        \item {Refactored YACC and LEX code in NetTran, enabling parallel input file parsing to enhance performance.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
