%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open Source Project}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Member \& Contributor} % Job title
    {LLVM Project} % Organization
    {Remote} % Location
    {June. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {LLVM Project is an open source project which provides modular and reusable compiler and toolchain technologies.}
        \item {Designed non-buffer mode in the internal implementation of I/O read.}
        \item {Fixed bugs in clang-format.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Contributor} % Job title
    {OpenPilot} % Organization
    {Remote} % Location
    {Feb. 2022 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Open-source advanced driver assistance system that works on 275+ car models of Toyota, Hyundai, Honda, and many other brands.}
        \item {Resolved an infinite-loop bug in the autopilot simulation by leveraging GDB to systematically narrow down the issue and implement a fix.}
        \item {Diagnosed and fixed a crash in the Docker environment by using Git to pinpoint the problematic commit, efficiently tracing root cause.}
        \item {Identified the root cause of a process crash—a bug in a third-party library—by utilizing Valgrind for in-depth memory analysis and debugging.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Contributor} % Job title
    {ArduPilot} % Organization
    {Remote} % Location
    {Oct. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Open-source autopilot system supporting many vehicle types: multi-copters, traditional helicopters, fixed wing aircraft, rovers and more.}
        \item {Refactored codebase to standardize coding style, improve readability, and enhance maintainability.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Contributor} % Job title
    {Ivy-llc} % Organization
    {Remote} % Location
    {Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Unified Machine Learning framework enabling data scientists to automatically convert and use ML models across popular ML frameworks.}
        \item {Resolved critical build errors in Docker images and enhanced documentation to improve clarity and usability.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
