%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Project}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {} % Job title
    {OSDI} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a lightweight operating system on the Raspberry Pi 3.}
        \item {Built a minimal shell interface over UART communication for user interaction on the SoC.}
        \item {Implemented a UART-based bootloader to load kernel images into appropriate memory locations.}
        \item {Configured the exception vector table and provided basic system calls read, write and sleep.}
        \item {Developed a memory management system, including a buddy allocator and a startup allocator.}
        \item {Designed and implemented a scheduler with context switching and register preservation via the stack.}
        \item {Achieved process isolation and virtual memory management using the MMU.}
        \item {Github: https://github.com/jackhong12/OSDI}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {} % Job title
    {Face Tracker} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and built a device that automatically adjusts a smartphone's orientation to keep the user centered in the camera frame.}
        \item {Developed high-priority interrupt service routines (ISRs) on the PIC18F4520 microcontroller to manage UART communication and receive real-time user position data.}
        \item {Implemented low-priority ISRs to decode motor encoder signals and generate PWM outputs for accurate pose control.}
        \item {Applied PID control theory to ensure smooth and responsive velocity control of a DC motor.}
        \item {Designed the mechanical structure using CAD software and fabricated the device using a CNC milling machine.}
        \item {Github: https://github.com/jackhong12/face-tracker}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
